\thetitle

### 2008-06-13 paper.tex
Moved TrafGen after CommonProps & CommonModels.

Two other unspecified constants appear in \Table{quantization}: $\beta$ and $\gamma$.
These parameters are non-linear scaling exponents that allows the quantization to smoothly shift from fine-grained resolution at the low end of the spectrum to coarse-grained resolution at the high end.
We have chosen $\beta=\fracx{1}{2.7}$ because it yields a desirable dynamic range response from bytes at the low end to megabytes at the high end.
Similarly, we have chosen $\gamma=\fracx{1}{3}$ because this choice provides resolution that scales smoothly from microseconds for small intervals to seconds for large intervals.

\subsection{Expression of Common Properties}
\label{sec:common-properties}

@@

\newfootnote{\onesnote}{%
Through out this paper, $\ones{}$ denotes a matrix of all ones, but the dimensions of the matrix must be inferred by context.
Where necessary, we disambiguate the dimensions by explicitly specifying the dimensions of the final matrix product.
}

From the matrices $\mat{Z}$ and $\mat{V}$ we can compute a variety of statistics about packet sizes and inter-packet intervals.
The flows vectors in the matrices may represent individual flows or composites of many flows.
% about packet sizes, total packet count, inter-packet intervals, and total duration for each representation vector, which may represent a single actual flow, or the composite behavior of many flows.
% We begin by expressing the vectors for total bytes, total packets and total duration for a matrix of flow representations, with size and interval matrices $\mat{Z}$ and $\mat{V}$.
The computations require knowing the values that each size of interval matrix column represents.
% The computed duration is approximate because information is irretrievably lost in the quantization process.
The vectors of representative values for $\mat{Z}$ and $\mat{V}$ respectively are:
\begin{align}
\vec{\sigma} &= \tuple{1,2,3,\dots,d_z} \\
\vec{\tau}   &= \tuple{\Df_\ival\left(k-\fracx{1}{2}\right)}_{k=1}^{d_v}.
\end{align}
The packet count, total byte and total duration vectors are computed as\onesnote
\begin{align}
\vec{\Sigma}_\pkts  &= \mat{Z}\trans{\ones{}} = \mat{V}\trans{\ones{}} \in \R^f \eqn{packet-count}\\
\vec{\Sigma}_\bytes &= \mat{Z}\trans{\vec{\sigma}} \in \R^f \eqn{total-bytes} \\
\vec{\Sigma}_\ivals &= \mat{V}\trans{\vec{\tau}} \in \R^f \eqn{total-duration}.
\end{align}
Here $\ones{}$ is a row vector of all ones.
Packet count and total bytes values are exact;
the total durations are only approximate because information is irretrievably lost in the quantization process.
Using these vectors of totals, we may readily compute the average packet sizes and inter-packet intervals:
\begin{align}
\vec{\mean{z}} &=
  \vec{\Sigma}_\bytes \eldiv \vec{\Sigma}_\pkts
  \phantom{= \mat{V}\trans{\vec{\tau}} \eldiv \mat{V}\trans{\ones{}}}
  \mathllap{= \mat{Z}\trans{\vec{\sigma}} \eldiv \mat{Z}\trans{\ones{}}} \\
\vec{\mean{v}} &=
  \phantom{\vec{\Sigma}_\bytes \eldiv \vec{\Sigma}_\pkts}
  \mathllap{\vec{\Sigma_{\ivals}} \eldiv \vec{\Sigma_{\pkts}}}
  = \mat{V}\trans{\vec{\tau}} \eldiv \mat{V}\trans{\ones{}}.
\end{align}
The symbol $\eldiv$ here represents element-wise division of vector coordinates, as it does in Matlab.

@@

The total number of source flows for each node is given by the vector $\trans{\mat{S}}\ones{f} \in \R^n$, and the total number of destination flows is given by $\trans{\mat{D}}\ones{f} \in \R^n$.
The number of flows between each pair of nodes in the network is expressed by the matrix product $\trans{\mat{S}}\mat{D}\in\R^{n \times n}$.
That is $(\trans{\mat{S}}\mat{D})_{ij}$ is the number of flows from node $i$ to node $j$.
Interpreting this sparse matrix as a weighted graph immediately yields the source-destination flow communication graph.
Similar graphs counting other quantities can readily be computed by inserting the appropriate weighting matrix.
For example, we may compute the packet transmission graph:
\begin{align}
\trans{\mat{S}}\diag(\vec{\Sigma}_\pkts)\mat{D}\in\R^{n \times n}.
\end{align}
Here $\vec{\Sigma}_\pkts$ is the byte vector defined in \Equation{packet-count}, and the ``$\diag$'' operator gives the square, diagonal matrix with the given vector of values on its diagonal.
Similar graphs for total bytes and total duration of flows may be computed using $\mat{\Sigma}_\bytes$ or $\mat{\Sigma}_\ival$ in place of $\mat{\Sigma}_\pkts$.

@@

The simplifying assumptions made by most traffic models can be classified into three categories. We use the terms \textit{uniformity}, \textit{marginality}, and \textit{conditionality} to describe these classes of assumptions. They are all assumptions about the ``sameness'' of aspects of network behaviors; they differ, however, in whether they make stipulations about uniformity within each flow, across all flows, or within groups of flows. In the following sections, we explore how various modeling concepts can be expressed in the framework of the general matrix model. Models are expressed as transformations that will convert arbitrary traffic matrix instances into similar ones that satisfy the model's assumptions. These transformations will later allow us to evaluate the effect of each model's simplifications on the realism of generated workloads.

>>>>

Two other unspecified constants appear in \Table{quantization}: $\beta$ and $\gamma$.
These parameters are non-linear scaling exponents that allows the quantization to smoothly shift from fine-grained resolution at the low end of the spectrum to coarse-grained resolution at the high end.
We have chosen $\beta=\fracx{1}{2.7}$ and $\gamma=\fracx{1}{3}$ because these values yield desirable dynamic ranges: from single bytes at the lower end to megabytes at the high end for flow sizes; from microseconds to seconds for intervals.

\subsection{Computation of Common Properties}
\label{sec:common-properties}

@@

\newfootnote{\onesnote}{%
Through out this paper, $\ones{}$ denotes a matrix of all ones; dimensions of the matrix are inferred by context.
Where necessary, we disambiguate the dimensions by explicitly specifying the dimensions of the final matrix product, as we do here.
}

From the matrices $\mat{Z}$ and $\mat{V}$ we can compute a variety of statistics about packet sizes and inter-packet intervals.
The flows vectors in the matrices may represent individual flows or composites of many flows.
% about packet sizes, total packet count, inter-packet intervals, and total duration for each representation vector, which may represent a single actual flow, or the composite behavior of many flows.
% We begin by expressing the vectors for total bytes, total packets and total duration for a matrix of flow representations, with size and interval matrices $\mat{Z}$ and $\mat{V}$.
The computations require knowing the values that each size of interval matrix column represents.
% The computed duration is approximate because information is irretrievably lost in the quantization process.
The vectors of representative values for $\mat{Z}$ and $\mat{V}$ respectively are:
\begin{align}
\vec{\sigma} &= \tuple{1,2,3,\dots,d_z} \\
\vec{\tau}   &= \tuple{\Df_\ival\left(k-\fracx{1}{2}\right)}_{k=1}^{d_v}.
\end{align}
The packet count, total byte and total duration vectors are computed as
\begin{align}
\vec{\Sigma}_\pkts  &= \mat{Z}\trans{\ones{}} = \mat{V}\trans{\ones{}} \in \R^f \eqn{packet-count}\\
\vec{\Sigma}_\bytes &= \mat{Z}\trans{\vec{\sigma}} \in \R^f \eqn{total-bytes} \\
\vec{\Sigma}_\ivals &= \mat{V}\trans{\vec{\tau}} \in \R^f \eqn{total-duration}.
\end{align}
Here $\ones{}$ is a row vector of all ones.\onesnote
Packet count and total bytes values are exact;
the total durations are only approximate because information is irretrievably lost in the quantization process.
Using these vectors of totals, we may readily compute the average packet sizes and inter-packet intervals:
\begin{align}
\vec{\mean{z}} &=
  \vec{\Sigma}_\bytes \eldiv \vec{\Sigma}_\pkts
  \phantom{= \mat{V}\trans{\vec{\tau}} \eldiv \mat{V}\trans{\ones{}}}
  \mathllap{= \mat{Z}\trans{\vec{\sigma}} \eldiv \mat{Z}\trans{\ones{}}} \\
\vec{\mean{v}} &=
  \phantom{\vec{\Sigma}_\bytes \eldiv \vec{\Sigma}_\pkts}
  \mathllap{\vec{\Sigma_{\ivals}} \eldiv \vec{\Sigma_{\pkts}}}
  = \mat{V}\trans{\vec{\tau}} \eldiv \mat{V}\trans{\ones{}}.
\end{align}
The symbol $\eldiv$ here represents element-wise division of vector coordinates, as it does in Matlab.

@@

The total number of source flows for each node is given by the vector $\trans{\mat{S}}\ones{f} \in \R^n$, and the total number of destination flows is given by $\trans{\mat{D}}\ones{f} \in \R^n$.
The number of flows between each pair of nodes in the network is expressed by the matrix product $\trans{\mat{S}}\mat{D}\in\R^{n \times n}$.
That is $(\trans{\mat{S}}\mat{D})_{ij}$ is the number of flows from node $i$ to node $j$.
Interpreting this sparse matrix as a weighted graph immediately yields the source-destination flow communication graph.
\Figure{trace-vs-uniform} gives two visual examples of such graphs.
Similar graphs counting other quantities can readily be computed by inserting the appropriate weighting matrix.
For example, we may compute the inter-node packet transmission graph:
\begin{align}
\trans{\mat{S}}\diag(\vec{\Sigma}_\pkts)\mat{D}\in\R^{n \times n}.
\end{align}
Here $\vec{\Sigma}_\pkts$ is the byte vector defined in \Equation{packet-count}, and the ``$\diag$'' operator gives the square, diagonal matrix with the given vector of values on its diagonal.
Similar graphs for total bytes and total duration of flows may be computed using $\mat{\Sigma}_\bytes$ or $\mat{\Sigma}_\ival$ in place of $\mat{\Sigma}_\pkts$.

@@

The simplifying assumptions made by most traffic models can be classified into three categories. We use the terms \textit{uniformity}, \textit{marginality}, and \textit{conditionality} to describe these classes of assumptions. They are all assumptions about the ``sameness'' of aspects of network behaviors; they differ, however, in whether they make stipulations about uniformity within each flow, across all flows, or within groups of flows. In the following sections, we explore how various modeling concepts can be expressed in the framework of the general matrix model. Models are expressed as transformations that convert arbitrary traffic matrix instances into similar ones that satisfy the model's assumptions. These transformations later allow us to evaluate the effect of each model's simplifications on the realism of generated workloads.
